Smart Drill-Down: Interactive Summarization of Relational Tables

### 2014-11-15 TableSummarization/Paper/exp.tex
small

>>>>

\agp{I propose using two sections: one is Qualitative Study, which will contain 4.2, 4.3, and 
Quantitiative Study, whcih will contain the rest of the sections.
For the quantitative study, mention that the goal of the experimental evaluation is to study
the impact of the two parameters on time and accuracy before you get into details.}

\agp{Additional experiments:
Maybe also good to fix mw, and show the performance with or without sampling,
and with or without a-priori (one rule per phase, for instance).
Also, would be good to see performance on increasing dataset size.
}
